MA_Results

### 2022-07-22 Markdown/Manuscript/Child_RMDs/MS_Aims.Rmd
stuck

- guidelines for quality implementation of OSHEMS;
- a framework for standardised and reproducible approaches to apply these guidelines to each component of the  **readyforwhatsnext** model; 
- a worked example of the first **readyforwhatsnext** model component developed using this framework.

>>>>

- a proposed set of guidelines for quality implementation of OSHEMS;
- a framework for standardised and reproducible application of these guidelines to the development of the  **readyforwhatsnext** model; 
- a worked example of the first **readyforwhatsnext** model component developed using the framework.

### 2022-07-22 Markdown/Manuscript/Child_RMDs/MS_Imp_Example.Rmd
stuck

# Application
We used framework toolkits to develop model code and datasets for implementing a utility mapping study that has previously been described [@Hamilton2021.07.07.21260129]. Table \@ref(tab:checktb) assesses that study against each TIMELY standard, 18 of which the study was able to meet. The two current standards where the study falls short are in reporting code coverage and including a user-interface. Both these items are current development priorities for our team.

>>>>

We used framework toolkits to develop model code and datasets for implementing a utility mapping study that has previously been described [@Hamilton2021.07.07.21260129]. Table \@ref(tab:checktb) assesses that study against each TIMELY standard, 18 of which the study was able to meet. The two current standards where the study falls short are in reporting code coverage and including a user-interface. Both these items are current development priorities for our team.

### 2022-07-22 Markdown/Manuscript/Child_RMDs/MS_Imp_Guidelines.Rmd
stuck

## Guidelines for OSHEMs
Adherence to explicit guidelines is an essential requirement for modelling in healthcare [@Erdemir2020]. Guidance for implementing OSHEMs remains scarce and piecemeal and needs to be improved [@Sampson2019].  Guidelines on health economic model transparency were published ten years ago [@Eddy2012] and made recommendations on documenting models; however, notably missing were recommendations on the sharing of model code and data. More recent and more general modelling guidance [@Erdemir2020] recommends the sharing of code and data through digital repository services <!-- such as GitHub [@github2007] and Zenodo [@Zenodo2013] --> and the use of version control systems <!-- such as Git [@git20XX].  -->

@@

### Transparent Models
A range of tools and practices are available to help make model code and data accessible, comprehensible and citable. The most efficient way to widely disseminate code and data may be to use existing open science infrastructure [@Erdemir2020] to make permanently accessible and uniquely identfied digital artefacts. <!-- Repositories such as Zenodo [@Zenodo2013] and Dataverse [@Dataverse2007] provide persistent storage solutions that generate a Digital Object Identifier (DOI) for each unique item. These repositories are a preferable solution for sharing citable code and data than transitory repositories such as corporate websites or GitHub where items can be deleted or relocated at any time [@sseditors2022]. Zenodo includes tools that automate integration with GitHub, which makes it easy for developers to maintain parallel code repositories - one for disseminating the most up to date development code and the other for archiving citable code releases. -->Model code and data also need to be clearly documented, potentially with different versions for technical and non-technical users [@Eddy2012]. <!-- Developers storing data in a Dataverse installation have access to multiple meta-data fields to document both a data collection and its individual constituent files.  --><!-- In R, code manuals and websites can be created with the aid of tools such as devtools [@devtools2021], sinew [@sinew2022], roxygen2 [@roxygen2021] and pkgdown [@pkgdown2022].  -->Consistent use of meaningful naming conventions when authoring code is recommended [@Wilson_2017; @Alarid2019]. Code can be made easier to follow by using the practices of abstraction [@8717448], where only simple, high level commands are routinely exposed to reviewers, and polymorphism [@7181447], where the same command (e.g. "simulate") can be reused to implement different algorithms of the same type. Programs to implement model analyses can be made comprehensible to even non-technical users through the use of literate programming techniques <!-- that use tools like RMarkdown [@xie2018r]  -->to render documents that integrate computer code with plain English descriptions.

@@

### Iterative Models
To avoid OSHEMs going stale - losing validity and usefulness with time - they should be routinely updated.  Each update of code and data should be uniquely identifiable and retrievable, a goal that can be facilitated by use of version control tools [@Erdemir2020].<!-- A number of tools and approaches can make the process of implementing and curating changes to model code and data more coherent and efficient.   <!-- Repositories such as Zenodo [@Zenodo2013] and Dataverse [@Dataverse2007] provide persistent access to all published versions of a dataset, each uniquely identifiable. For code, use of version control tools like Git [@git20XX] can ensure that the entire development history of a project is organised so that each version is distinguishable and retrievable by developers. The online platform GitHub [@github2007] can make this version history accessible to anyone. -->Labeling each change using semantic versioning [@semver20xx] conventions can signal the potential importance of an update to users of model code and data. <!-- For R code, the usethis [@usethis2021] package can be used to partially automate version number increments using the convention Major.Minor.Patch.Development (e.g. ExampleSoftware v1.1.1.1). Datasets stored on the Harvard Dataverse use the simpler Major.Minor convention.  -->Continuous integration [@CI2017] tools can help verify that each code update passes multiple quality tests. <!-- OSHEMs developed in R can take advantage of templates provided by devtools [@devtools2021] and pkgdown [@pkgdown2022] to run continuous integration checks on GitHub.  --><!-- These tests can include those of units (do individual functions produce expected output?), documentation (does documentation render correctly?; can all example workflows be executed?) and installation (can the software be successfully deployed on multiple types of operating system?).  -->
Finally, using deprecation conventions that take an informative and staged approach to retiring old code and data reduces the risk that model revisions have unintended consequences on third party users.  -->
<!-- The package lifeycle [@lifecycle2021] provides tools for R developers to consistently deprecate their code. -->

@@

### Modular Models
Modular health economic models link multiple self-contained components that can be independently reused and extended by other projects [@Trauer2017;@Urach2013]. Many types of mental health data are highly sensitive with strict confidentiality requirements. For this reason, not all data included in some mental health models can be made widely available for others to re-use. A modular approach that ensures that model code and data are decoupled (stored in different files) can help model developers to restrict access to confidential model data, while providing open access to all other model components. An important consideration when combining model components (or modules) is to ensure that interactions between two modules do not compromise the validity of either. Using the coding practice of encapsulation [@8717448] can help ensure that model modules can be safely combined [@ready4oop2022].

@@

### Epitomising Models
A key challenge to generalising health economic models is that they are typically developed to inform a decision problem with a highly specific jurisdictional context. However, a number of choices about how these models are implemented can significantly increase the re-usability of model code in other contexts.

@@

### Licensed Models
```{r echo = F}
gpl_pc_dbl <- get_license_share("GPL")
```

@@

### Yielding Models
OSHEMs can be time and skills intensive for modellers to develop - but they should be easy for others to use. Statistical models are a common output of health economic evaluations, but they are often not reported in a format that enables others to confidently and reliably re-use them [@Kearns2013]. Open source approaches can help address this by disseminating code artefacts that enable easy and appropriate use of a statistical model to make predictions with new data. However, great care must be exercised when doing so if models are derived from data on human subjects as some software artefacts by default contain a copy of the source dataset. Such dataset copies must therefore be replaced (for example, with synthetic data) and the amended artefact's predictive performance then retested before any public release. Another way to make OSHEMs easier to use is to develop simple user-interfaces for non-technical users. 
<!-- In R, such user-interfaces are typically developed with the Shiny package, for which a tutorial aimed at health economists is available [@SmithR2020]. -->

>>>>

Adherence to explicit guidelines is an essential requirement for modelling in healthcare [@Erdemir2020]. Guidance for implementing OSHEMs remains scarce and piecemeal and needs to be improved [@Sampson2019].  Guidelines on health economic model transparency were published ten years ago [@Eddy2012] and made recommendations on documenting models; however, notably missing were recommendations on the sharing of model code and data. More recent and more general modelling guidance [@Erdemir2020] recommends the sharing of code and data through digital repository services <!-- such as GitHub [@github2007] and Zenodo [@Zenodo2013] --> and the use of version control systems <!-- such as Git [@git20XX].  -->

@@

## Transparent Models
A range of tools and practices are available to help make model code and data accessible, comprehensible and citable. The most efficient way to widely disseminate code and data may be to use existing open science infrastructure [@Erdemir2020] to make permanently accessible and uniquely identfied digital artefacts. <!-- Repositories such as Zenodo [@Zenodo2013] and Dataverse [@Dataverse2007] provide persistent storage solutions that generate a Digital Object Identifier (DOI) for each unique item. These repositories are a preferable solution for sharing citable code and data than transitory repositories such as corporate websites or GitHub where items can be deleted or relocated at any time [@sseditors2022]. Zenodo includes tools that automate integration with GitHub, which makes it easy for developers to maintain parallel code repositories - one for disseminating the most up to date development code and the other for archiving citable code releases. -->Model code and data also need to be clearly documented, potentially with different versions for technical and non-technical users [@Eddy2012]. <!-- Developers storing data in a Dataverse installation have access to multiple meta-data fields to document both a data collection and its individual constituent files.  --><!-- In R, code manuals and websites can be created with the aid of tools such as devtools [@devtools2021], sinew [@sinew2022], roxygen2 [@roxygen2021] and pkgdown [@pkgdown2022].  -->Consistent use of meaningful naming conventions when authoring code is recommended [@Wilson_2017; @Alarid2019]. Code can be made easier to follow by using the practices of abstraction [@8717448], where only simple, high level commands are routinely exposed to reviewers, and polymorphism [@7181447], where the same command (e.g. "simulate") can be reused to implement different algorithms of the same type. Programs to implement model analyses can be made comprehensible to even non-technical users through the use of literate programming techniques <!-- that use tools like RMarkdown [@xie2018r]  -->to render documents that integrate computer code with plain English descriptions.

@@

## Iterative Models
To avoid OSHEMs going stale - losing validity and usefulness with time - they should be routinely updated.  Each update of code and data should be uniquely identifiable and retrievable, a goal that can be facilitated by use of version control tools [@Erdemir2020].<!-- A number of tools and approaches can make the process of implementing and curating changes to model code and data more coherent and efficient.   <!-- Repositories such as Zenodo [@Zenodo2013] and Dataverse [@Dataverse2007] provide persistent access to all published versions of a dataset, each uniquely identifiable. For code, use of version control tools like Git [@git20XX] can ensure that the entire development history of a project is organised so that each version is distinguishable and retrievable by developers. The online platform GitHub [@github2007] can make this version history accessible to anyone. -->Labeling each change using semantic versioning [@semver20xx] conventions can signal the potential importance of an update to users of model code and data. <!-- For R code, the usethis [@usethis2021] package can be used to partially automate version number increments using the convention Major.Minor.Patch.Development (e.g. ExampleSoftware v1.1.1.1). Datasets stored on the Harvard Dataverse use the simpler Major.Minor convention.  -->Continuous integration [@CI2017] tools can help verify that each code update passes multiple quality tests. <!-- OSHEMs developed in R can take advantage of templates provided by devtools [@devtools2021] and pkgdown [@pkgdown2022] to run continuous integration checks on GitHub.  --><!-- These tests can include those of units (do individual functions produce expected output?), documentation (does documentation render correctly?; can all example workflows be executed?) and installation (can the software be successfully deployed on multiple types of operating system?).  -->
Finally, using deprecation conventions that take an informative and staged approach to retiring old code and data reduces the risk that model revisions have unintended consequences on third party users.  -->
<!-- The package lifeycle [@lifecycle2021] provides tools for R developers to consistently deprecate their code. -->

@@

## Modular Models
Modular health economic models link multiple self-contained components that can be independently reused and extended by other projects [@Trauer2017;@Urach2013]. Many types of mental health data are highly sensitive with strict confidentiality requirements. For this reason, not all data included in some mental health models can be made widely available for others to re-use. A modular approach that ensures that model code and data are decoupled (stored in different files) can help model developers to restrict access to confidential model data, while providing open access to all other model components. An important consideration when combining model components (or modules) is to ensure that interactions between two modules do not compromise the validity of either. Using the coding practice of encapsulation [@8717448] can help ensure that model modules can be safely combined [@ready4oop2022].

@@

## Epitomising Models
A key challenge to generalising health economic models is that they are typically developed to inform a decision problem with a highly specific jurisdictional context. However, a number of choices about how these models are implemented can significantly increase the re-usability of model code in other contexts.

@@

## Licensed Models
```{r echo = F}
gpl_pc_dbl <- get_license_share("GPL")
```

@@

## Yielding Models
OSHEMs can be time and skills intensive for modellers to develop - but they should be easy for others to use. Statistical models are a common output of health economic evaluations, but they are often not reported in a format that enables others to confidently and reliably re-use them [@Kearns2013]. Open source approaches can help address this by disseminating code artefacts that enable easy and appropriate use of a statistical model to make predictions with new data. However, great care must be exercised when doing so if models are derived from data on human subjects as some software artefacts by default contain a copy of the source dataset. Such dataset copies must therefore be replaced (for example, with synthetic data) and the amended artefact's predictive performance then retested before any public release. Another way to make OSHEMs easier to use is to develop simple user-interfaces for non-technical users. 
<!-- In R, such user-interfaces are typically developed with the Shiny package, for which a tutorial aimed at health economists is available [@SmithR2020]. -->

### 2022-07-22 Markdown/Manuscript/Child_RMDs/MS_Intro_Short.Rmd
stuck

<!-- `r ifelse(is.na(params$X@background_1L_chr),"",params$X@background_1L_chr)`  -->
Health economic computational models have become essential tools for health policy development [@dakin2015influence; @Erdemir2020]. Although influential and widely used, these models routinely contain errors [@Radeva2020], are rarely adequately validated [@Ghabri2019], can be difficult to reproduce [@Jalali2021; @McManus2019; @Bermejo2017] and are likely to be infrequently updated or revised [@Sampson2017]. To help address these issues, there is growing support for greater use of open source health economic models (OSHEMs) that grant liberal permissions to access and re-use model source code and data [@Pouwels2022].

Collaborations across multiple modelling teams that include the ability to re-use and extend one another's work can make complex modelling projects more tractable [@Arnold2010]. Reference models intended for multiple-applications and re-use by different modelling teams have been advocated for [@Afzali2013] but require greater investments in model transparency and validation [@Eddy2012; @Feenstra2022]. Systems modelling approaches may be particularly relevant to exploring some public health economics topics  [@SQUIRES2016588] but such complex models may be more prone to error [@Saltelli2019]. To retain and improve their utility as decision aids, health economic models require updating and refinement as new evidence emerges and decision contexts change [@Jenkins2021].

Open source approaches have been recommended to help develop a mental health field that rarely models complex dynamic systems [@RN73]. Economic studies predominantly examining the affordability and value for money of individual mental health programs [@RN34]. Yet such single purpose models that assume static systems may be inadequate for the decision support needs of policymakers and service planners [@PC2020; @Occhipinti2021]. 
<!-- and for mental health specifically [@Occhipinti2021],  -->
<!-- could provide greater insight about inter-dependencies between candidate policies and the dynamic nature of the mental health systems planning context. Dynamic systems methods might provide the foundations for developing   -->
<!-- and models designed for multiple purposes r -->

>>>>

<!-- `r ifelse(is.na(params$X@background_1L_chr),"",params$X@background_1L_chr)`  -->
Computational models have become essential tools for health policy development [@dakin2015influence; @Erdemir2020]. Although influential and widely used, these models routinely contain errors [@Radeva2020], are rarely adequately validated [@Ghabri2019], can be difficult to reproduce [@Jalali2021; @McManus2019; @Bermejo2017] and are likely to be infrequently updated or revised [@Sampson2017]. To help address these issues, there is growing support for greater use of open source health economic models (OSHEMs) that grant liberal permissions to access and re-use model source code and data [@Pouwels2022].

Enabling multiple modelling teams to collaboratively re-use, test and extend one another's work can make complex modelling projects more tractable [@Arnold2010]. Recommendations to update and refine health economic models as new evidence emerges and decision contexts change [@Jenkins2021], adopt systems modelling approaches for public health economics topics [@SQUIRES2016588] and to develop multiple-application or reference models for re-use by different modelling teams [@Afzali2013] all involve resourcing and quality assurance challenges. For example, complex models may be more prone to error [@Saltelli2019] and reference models require greater investments in model transparency and validation [@Eddy2012; @Feenstra2022].

Open source approaches have been recommended to help develop a mental health modelling field that rarely explores complex dynamic systems [@RN73]. Mental health economic studies predominantly examine the affordability and value for money of individual programs [@RN34]. Yet single purpose models that assume static systems may be inadequate for the decision support needs of policymakers and service planners [@PC2020; @Occhipinti2021]. 
<!-- and for mental health specifically [@Occhipinti2021],  -->
<!-- could provide greater insight about inter-dependencies between candidate policies and the dynamic nature of the mental health systems planning context. Dynamic systems methods might provide the foundations for developing   -->
<!-- and models designed for multiple purposes r -->

### 2022-07-22 Markdown/Manuscript/Child_RMDs/MS_Results.Rmd
stuck

```{r child="../Child_RMDs/XX_Funs.Rmd", echo=FALSE}
```
```{r child="../Child_RMDs/MS_Tables.Rmd", echo=FALSE}
```
```{r child="../Child_RMDs/MS_Figures.Rmd", echo=FALSE}
```
<!-- Add child RMDs for results content -->
```{r child="../Child_RMDs/MS_Imp_Guidelines.Rmd", echo=FALSE}
```
```{r child="../Child_RMDs/MS_Imp_Toolkit.Rmd", echo=FALSE}
```
```{r child="../Child_RMDs/MS_Imp_Example.Rmd", echo=FALSE}
```

>>>>

```{r child="../Child_RMDs/XX_Funs.Rmd", echo=FALSE}
```
```{r child="../Child_RMDs/MS_Tables.Rmd", echo=FALSE}
```
```{r child="../Child_RMDs/MS_Figures.Rmd", echo=FALSE}
```
<!-- Add child RMDs for results content -->
# Guidelines
```{r child="../Child_RMDs/MS_Imp_Guidelines.Rmd", echo=FALSE}
```
# Framework
```{r child="../Child_RMDs/MS_Imp_Toolkit.Rmd", echo=FALSE}
```
# Application
```{r child="../Child_RMDs/MS_Imp_Example.Rmd", echo=FALSE}
```
